---
title: "Final Project"
author: "Isis Williams"
output: 
  flexdashboard::flex_dashboard:
    theme: spacelab
    source: embed
    smart: false
runtime: shiny
---

```{r include = FALSE}

# LOAD PACKAGES

library(DT)
library(ggmap)
library(shiny)
library(knitr)
library(pander)
library(leaflet)
library(viridis)
library(rsconnect)
library(tidyverse)
library(flexdashboard)



# READ IN DATA

url <- paste0("https://github.com/DS4PS/Data-",
              "Science-Class/blob/master/DATA",
              "/TempeTrafficAccidents.rds?raw=true")

dat <- readRDS(gzcon(url(url)))



# DATA PREPROCESSING I: INJURIES & FATALITIES

dat        <- na.omit(dat)                                       # Remove NAs
dat$fatal  <- dat$Totalfatalities > 0                            # 1+ fatalities
dat$inj    <- dat$Totalinjuries > 0 & dat$Totalfatalities == 0   # 1+ injury, 0 fatal
dat$nohurt <- dat$Totalfatalities + dat$Totalinjuries == 0       # Harmless

date.vec   <- strptime(dat$DateTime, format = "%m/%d/%y %H:%M")  # Datetime variables
dat$hour   <- format(date.vec, format = "%H") %>% as.numeric()
dat$month  <- format(date.vec, format = "%b")
dat$day    <- format(date.vec, format = "%a")
dat$day365 <- format(date.vec, format = "%j")
dat$week   <- format(date.vec, format = "%V")



# DATA PREPROCESSING II: NAMED INTERVALS OF TIME

dat <- dat %>% 
  mutate(time.of.day = case_when(hour >= 6 & hour <= 9 ~ "Morning Commute", 
                                 hour >= 16 & hour <= 19 ~ "Evening Commute", 
                                 hour >= 14 & hour <= 15 ~ "School Pickup", 
                                 hour >= 9 & hour <= 13 ~ "Work", 
                                 hour >= 20 & hour <= 23 ~ "Night", 
                                 hour <= 5 & hour >= 0 ~ "Midnight to Dawn"))

dat$harm <- ifelse( dat$Totalinjuries > 0 | dat$Totalfatalities > 0, "Harm", "No Harm" )



# DATA PREPROCESSING III: PERMUTATIONS OF INEBRIATION

dat <- dat %>% 
  mutate(d1.substance = case_when(AlcoholUse_Drv1 == "Alcohol" & 
                                  DrugUse_Drv1 == "No Apparent Influence" ~ "Alcohol", 
                                  AlcoholUse_Drv1 == "No Apparent Influence" & 
                                  DrugUse_Drv1 == "Drugs" ~ "Drugs", 
                                  AlcoholUse_Drv1 == "Alcohol" & 
                                  DrugUse_Drv1 == "Drugs" ~ "Alcohol and Drugs", 
                                  AlcoholUse_Drv1 == "No Apparent Influence" & 
                                  DrugUse_Drv1 == "No Apparent Influence" ~ "No Apparent
                                  Influence"))

dat <- dat %>% 
  mutate( d2.substance = case_when(AlcoholUse_Drv2 == "Alcohol" & 
                                   DrugUse_Drv2 == "No Apparent Influence" ~ "Alcohol", 
                                   AlcoholUse_Drv2 == "No Apparent Influence" & 
                                   DrugUse_Drv2 == "Drugs" ~ "Drugs", 
                                   AlcoholUse_Drv2 == "Alcohol" & 
                                   DrugUse_Drv2 == "Drugs" ~ "Alcohol and Drugs", 
                                   AlcoholUse_Drv2 == "No Apparent Influence" & 
                                   DrugUse_Drv2 == "No Apparent Influence" ~ "No Apparent
                                   Influence"))



# DATA PREPROCESSING IV: AGE CATEGORIES

dat$age.cat <- case_when(dat$Age_Drv1 >= 0 & 
                         dat$Age_Drv1 <= 18 ~ "Youth", 
                         dat$Age_Drv1 >= 19 & 
                         dat$Age_Drv1 <= 25 ~ "Young Adult", 
                         dat$Age_Drv1 >= 26 & 
                         dat$Age_Drv1 <= 64 ~ "Adult", 
                         dat$Age_Drv1 >= 65 ~ "Senior")
```

# Traffic Accidents By Day and Time

## Inputs {.sidebar}

```{r}
checkboxGroupInput("days", label = h3("Day of Week"), 
    choices = list("Monday"    = "Mon", 
                   "Tuesday"   = "Tue", 
                   "Wednesday" = "Wed", 
                   "Thursday"  = "Thu",
                   "Friday"    = "Fri",
                   "Saturday"  = "Sat",
                   "Sunday"    = "Sun" ),
    selected = c("Fri","Sat","Sun"))

sliderInput("hour", label = h3("Time of Day"), 
            min = 0, max = 23, value = c(6, 12))

# parameters

```

## Outputs

### Traffic Accidents By Day and Time

```{r}

# LEAFLET MAPPING

renderLeaflet({
  
  days.of.week <- input$days    # Vector of checked days
  start.time <- input$hour[1]   # Slider input of lower time range
  end.time  <-  input$hour[2]   # Slider input of upper time range
  
  d2 <- dat %>%
    filter(day %in% input$days, 
           hour >= start.time & hour <= end.time)
  
  d2$col.vec <- ifelse( d2$nohurt, "gray20", 
                        ifelse(d2$inj, "steelblue", "darkorange") ) 
  
  point.size <- d2$Totalinjuries + d2$Totalfatalities

  crash.details <- paste0("Time: ", d2$DateTime, "<br>",
                          "Total Fatalities: ", d2$Totalfatalities, "<br>",
                          "Total Injuries: ", d2$Totalinjuries, "<br>",
                          "Collision type: ", d2$Collisionmanner)
  
  tempe <- leaflet( ) %>% 
    addProviderTiles("CartoDB.Positron")  %>%
    setView(lng = -111.9278, 
            lat = 33.39951, 
            zoom = 13)
  
  
  addCircles(tempe, 
             lng = d2$Longitude, 
             lat = d2$Latitude,
             fillColor = d2$col.vec, 
             fillOpacity = 0.5, 
             stroke = FALSE, 
             radius = 50*(1+0.33*point.size),
             popup = crash.details)


})

```

# Driver Characteristics {data-orientation="rows"}

## Sidebar {.sidebar}

Driver Characteristics

```{r}

sliderInput(inputId = "d1age", 
            label = h4("Driver 1 Age"), 
            min = 15, 
            max = 100, 
            value = c(18,36) )

sliderInput(inputId = "d2age", 
            label = h4("Driver 2 Age"), 
            min = 15, 
            max = 100, 
            value = c(18,36) )

selectInput(inputId = "d1gender", 
            label = h4("Driver 1 Gender"), 
            choices = c("Male","Female", "Unknown"), 
            selected = c("Male"))

selectInput(inputId = "d2gender", 
            label = h4("Driver 2 Gender"), 
            choices = c("Male","Female", "Unknown"), 
            selected = c("Male"))

radioButtons(inputId = "d1pedcy", 
             label = h4("Driver 1 Transportation"),
             choices = c("Driver", "Pedalcyclist", "Pedestrian"), 
             selected = c("Driver"))

radioButtons(inputId = "d2pedcy", 
             label = h4("Driver 2 Transportation"),
             choices = c("Driver", "Pedalcyclist", "Pedestrian"), 
             selected = c("Driver"))

```

## Row

### Number of Crashes

```{r}

renderValueBox({
  
  d2 <- dat %>%
    filter(Age_Drv1 >= input$d1age[1] & Age_Drv1 <= input$d1age[2], 
           Age_Drv2 >= input$d2age[1] & Age_Drv2 <= input$d2age[2], 
           Gender_Drv1 %in% input$d1gender, 
           Gender_Drv2 %in% input$d2gender, 
           Unittype_One %in% input$d1pedcy, 
           Unittype_Two %in% input$d2pedcy )
  
  crashes <- count( d2 )
  
  valueBox(crashes, 
           icon = "fa-pencil",
           color = ifelse( crashes > 50, "danger", "primary") )
  
})

```

### Total Injuries

```{r}

renderValueBox({
  
  d2 <- dat %>%
    filter(Age_Drv1 >= input$d1age[1] & Age_Drv1 <= input$d1age[2], 
           Age_Drv2 >= input$d2age[1] & Age_Drv2 <= input$d2age[2], 
           Gender_Drv1 %in% input$d1gender, 
           Gender_Drv2 %in% input$d2gender, 
           Unittype_One %in% input$d1pedcy, 
           Unittype_Two %in% input$d2pedcy)
  
  total.injuries <- sum(d2$Totalinjuries)
  
  valueBox(total.injuries, 
           icon = "fa-angry",
           color = ifelse(total.injuries > 30, "danger", "primary" ))

  })

```

### Total Fatalities

```{r}

renderValueBox({
  
  d2 <- dat %>%
    filter(Age_Drv1 >= input$d1age[1] & Age_Drv1 <= input$d1age[2], 
           Age_Drv2 >= input$d2age[1] & Age_Drv2 <= input$d2age[2], 
           Gender_Drv1 %in% input$d1gender, 
           Gender_Drv2 %in% input$d2gender, 
           Unittype_One %in% input$d1pedcy, 
           Unittype_Two %in% input$d2pedcy)

  total.fatalities <- sum(d2$Totalfatalities)
  
  valueBox(total.fatalities, 
           icon = "fa-briefcase-medical",
           color = ifelse(total.fatalities > 10, "danger", "primary"))
  
})

```

### Rate of Harm

```{r}

renderValueBox({
  
  d2 <- dat %>%
    filter(Age_Drv1 >= input$d1age[1] & Age_Drv1 <= input$d1age[2], 
           Age_Drv2 >= input$d2age[1] & Age_Drv2 <= input$d2age[2], 
           Gender_Drv1 %in% input$d1gender, 
           Gender_Drv2 %in% input$d2gender, 
           Unittype_One %in% input$d1pedcy, 
           Unittype_Two %in% input$d2pedcy)
  
  rate.of.harm <- round(length(which(d2$harm == "Harm"))/count(d2), 3)
  
  valueBox(rate.of.harm, 
           icon = "fa-pencil",
           color = ifelse(rate.of.harm > 0.5, "danger", "primary"))
  
})

```

## Outputs

### Traffic Accidents by Driver Characteristics

```{r}

renderLeaflet({
  
  # days.of.week <- input$days    # vector will all checked values
  # start.time <- input$hour[1]   # sliderInput lower value
  # end.time  <-  input$hour[2] 
  
  d2 <- dat %>%
    filter(Age_Drv1 >= input$d1age[1] & Age_Drv1 <= input$d1age[2], 
           Age_Drv2 >= input$d2age[1] & Age_Drv2 <= input$d2age[2], 
           Gender_Drv1 %in% input$d1gender, 
           Gender_Drv2 %in% input$d2gender, 
           Unittype_One %in% input$d1pedcy, 
           Unittype_Two %in% input$d2pedcy)
  
  d2$col.vec <- ifelse(d2$nohurt, "gray20", 
                       ifelse(d2$inj, "steelblue", "darkorange") )              
    
  point.size <- d2$Totalinjuries + d2$Totalfatalities

  crash.details <- paste0("Time: ", d2$DateTime, "<br>",
                          "Total Fatalities: ", d2$Totalfatalities, "<br>",
                          "Total Injuries: ", d2$Totalinjuries, "<br>",
                          "Collision type: ", d2$Collisionmanner)
  
  tempe <- leaflet() %>% 
    addProviderTiles( "CartoDB.Positron" )  %>%
    setView( lng=-111.9278, lat=33.39951, zoom=13 )
  
  
  addCircles(tempe, lng=d2$Longitude, lat=d2$Latitude,
             fillColor=d2$col.vec, fillOpacity=0.5, 
             stroke=F, radius=50*(1+0.33*point.size),
             popup=crash.details )


})

```

# Comparisons {data-orientation="rows"}

## Sidebar {.sidebar}

Driver Characteristics

```{r}

sliderInput(inputId = "driver.1.age", 
            label = h4("Driver 1 Age"), 
            min = 15, 
            max = 100, 
            value = c(18,36))

sliderInput(inputId = "driver.2.age", 
            label = h4("Driver 2 Age"), 
            min = 15, 
            max = 100, 
            value = c(18,36))

selectInput(inputId = "driver.1.gender", 
            label = h4("Driver 1 Gender"), 
            choices = c("Male","Female", "Unknown"), 
            selected = c("Male"))

selectInput(inputId = "driver.2.gender", 
            label = h4("Driver 2 Gender"), 
            choices = c("Male","Female", "Unknown"), 
            selected = c("Male"))

radioButtons(inputId = "driver.1.pedcy", 
             label = h4("Driver 1 Transportation"),
             choices = c("Driver", "Pedalcyclist", "Pedestrian"), 
             selected = c("Driver"))

radioButtons(inputId = "driver.2.pedcy", 
             label = h4("Driver 2 Transportation"),
             choices = c("Driver", "Pedalcyclist", "Pedestrian"), 
             selected = c("Driver"))

```

## Row

### Number of Crashes

```{r}

renderValueBox({
  
  d2 <- dat %>%
    filter(Age_Drv1 >= input$d1age[1] & Age_Drv1 <= input$d1age[2], 
           Age_Drv2 >= input$d2age[1] & Age_Drv2 <= input$d2age[2], 
           Gender_Drv1 %in% input$d1gender, 
           Gender_Drv2 %in% input$d2gender, 
           Unittype_One %in% input$d1pedcy, 
           Unittype_Two %in% input$d2pedcy )
  
  crashes <- count( d2 )
  
  valueBox(crashes, 
           icon = "fa-pencil",
           color = ifelse( crashes > 50, "danger", "primary") )
  
})

```

### Total Injuries

```{r}

renderValueBox({
  
  d2 <- dat %>%
    filter(Age_Drv1 >= input$d1age[1] & Age_Drv1 <= input$d1age[2], 
           Age_Drv2 >= input$d2age[1] & Age_Drv2 <= input$d2age[2], 
           Gender_Drv1 %in% input$d1gender, 
           Gender_Drv2 %in% input$d2gender, 
           Unittype_One %in% input$d1pedcy, 
           Unittype_Two %in% input$d2pedcy)
  
  total.injuries <- sum(d2$Totalinjuries)
  
  valueBox(total.injuries, 
           icon = "fa-angry",
           color = ifelse(total.injuries > 30, "danger", "primary"))
  
})

```

### Total Fatalities

```{r}

renderValueBox({
  
  d2 <- dat %>%
    filter(Age_Drv1 >= input$d1age[1] & Age_Drv1 <= input$d1age[2], 
           Age_Drv2 >= input$d2age[1] & Age_Drv2 <= input$d2age[2], 
           Gender_Drv1 %in% input$d1gender, 
           Gender_Drv2 %in% input$d2gender, 
           Unittype_One %in% input$d1pedcy, 
           Unittype_Two %in% input$d2pedcy)

  total.fatalities <- sum(d2$Totalfatalities)
  
  valueBox(total.fatalities, 
           icon = "fa-briefcase-medical",
           color = ifelse(total.fatalities > 10, "danger", "primary"))
  
})

```

### Rate of Harm

```{r}

renderValueBox({
  
  d2 <- dat %>%
    filter(Age_Drv1 >= input$d1age[1] & Age_Drv1 <= input$d1age[2], 
           Age_Drv2 >= input$d2age[1] & Age_Drv2 <= input$d2age[2], 
           Gender_Drv1 %in% input$d1gender, 
           Gender_Drv2 %in% input$d2gender, 
           Unittype_One %in% input$d1pedcy, 
           Unittype_Two %in% input$d2pedcy)
  
  rate.of.harm <- round(length(which(d2$harm == "Harm"))/count(d2), 3)
  
  valueBox(rate.of.harm, 
           icon = "fa-pencil",
           color = ifelse(rate.of.harm > 0.5, "danger", "primary"))
  
})

```

## Column

### Driver 1

```{r}

renderLeaflet({
  
  # days.of.week <- input$days    # vector will all checked values
  # start.time <- input$hour[1]   # sliderInput lower value
  # end.time  <-  input$hour[2] 
  
  d10 <- dat %>%
    filter(Age_Drv1 >= input$driver.1.age[1] & Age_Drv1 <= input$driver.1.age[2], 
           Gender_Drv1 %in% input$driver.1.gender, 
           Unittype_One %in% input$driver.1.pedcy )
  
  d10$col.vec <- ifelse(d10$nohurt, "gray20", 
                        ifelse(d10$inj, "steelblue", "darkorange") )              
    
  point.size <- d10$Totalinjuries + d10$Totalfatalities

  crash.details <- paste0("Time: ", d10$DateTime, "<br>",
                          "Total Fatalities: ", d10$Totalfatalities, "<br>",
                          "Total Injuries: ", d10$Totalinjuries, "<br>",
                          "Collision type: ", d10$Collisionmanner)
  
  tempe <- leaflet() %>% 
    addProviderTiles("CartoDB.Positron") %>%
    setView(lng = -111.9278, 
            lat = 33.39951, 
            zoom = 13)
  
  addCircles(tempe, 
             lng = d10$Longitude, 
             lat = d10$Latitude,
             fillColor = d10$col.vec, 
             fillOpacity = 0.5, 
             stroke = F, 
             radius = 50*(1 + 0.33 * point.size),
             popup = crash.details)


})
```

### Driver 2

```{r}

renderLeaflet({
  
  # days.of.week <- input$days    # vector will all checked values
  # start.time <- input$hour[1]   # sliderInput lower value
  # end.time  <-  input$hour[2] 
  
  d11 <- dat %>%
    filter(Age_Drv2 >= input$driver.2.age[1] & Age_Drv2 <= input$driver.2.age[2], 
           Gender_Drv2 %in% input$driver.2.gender, 
           Unittype_Two %in% input$driver.2.pedcy)
  
  d11$col.vec <- ifelse(d11$nohurt, "gray20", 
                        ifelse(d11$inj, "steelblue", "darkorange"))
  
  point.size2 <- d11$Totalinjuries + d11$Totalfatalities

  crash.details2 <- paste0("Time: ", d11$DateTime, "<br>",
                           "Total Fatalities: ", d11$Totalfatalities, "<br>",
                           "Total Injuries: ", d11$Totalinjuries, "<br>",
                           "Collision type: ", d11$Collisionmanner)
  
  tempe2 <- leaflet() %>% 
    addProviderTiles("CartoDB.Positron") %>%
    setView(lng = -111.9278, 
            lat = 33.39951, 
            zoom = 13)
  
  addCircles(tempe2, 
             lng = d11$Longitude, 
             lat = d11$Latitude,
             fillColor = d11$col.vec, 
             fillOpacity = 0.5, 
             stroke = F, 
             radius = 50 * (1 + 0.33 * point.size2),
             popup = crash.details2 )

})

```

# Accident Characteristics

## Inputs {.sidebar}

```{r}
selectInput(
      inputId = "D1substanceFilter", 
      label = h3("Substance Driver"),
      choices = c("All", "Alcohol", "Drugs", "Alcohol and Drugs", "No Apparent Influence"),
      selected = "All")

selectInput(
      inputId =  "timeOfDay", 
      label = h3("Time of Day"),
      choices = c("All", "Morning Commute", "Evening Commute", "School Pickup", "Work", "Night", "Midnight to Dawn"),
      selected = "All")

```

## Outputs

### Substance use: Drugs, alcohol

```{r}
renderLeaflet({
  
  
  filtered_data <- dat %>%
    filter((input$D1substanceFilter == "All" | d1.substance == input$D1substanceFilter) &
           (input$timeOfDay == "All" | time.of.day == input$timeOfDay))
  
  col.vec <- ifelse(filtered_data$nohurt, 
                    "gray25", 
                    ifelse(filtered_data$inj, 
                           "purple", 
                           "red"))  
  
  point.size <- filtered_data$Totalinjuries + filtered_data$Totalfatalities
  
  crash.details <- paste0("Time: ", filtered_data$DateTime, "<br>",
                          "Total Fatalities: ", filtered_data$Totalfatalities, "<br>",
                          "Total Injuries: ", filtered_data$Totalinjuries, "<br>",
                          "Collision type: ", filtered_data$Collisionmanner)
  
  tempe <- leaflet(filtered_data) %>% 
    addProviderTiles("CartoDB.Positron") %>%
    setView(lng = -111.9278, lat = 33.4265, zoom = 13)
  
  tempe %>% 
    addCircles(lng = ~Longitude, 
               lat = ~Latitude,
               fillColor = ~col.vec, 
               fillOpacity = 0.5, 
               stroke = FALSE, 
               radius = ~50 * (1 + 0.33 * point.size),
               popup = ~crash.details) %>% 
    addLegend("topright",
              colors = c("red", "purple"),
              labels = c("Fatal", "Injuries"),
              title = "Accident Severity",
              opacity = 1)
  
})
```

# Weather and Light Characteristics

## Inputs {.sidebar}

```{r}

radioButtons(inputId = "Lightcondition", 
             label = h4("Light Condition"), 
             choices = c("Dark Unknown Lighting","Dark Lighted","Dusk", "Dawn",
                         "Daylight","Unknown"), 
             selected = "Daylight")


radioButtons(inputId = "Weather", 
             label = h4("Weather Condition"), 
             choices = c("Cloudy", "Clear", "Rain","Fog smog smoke",
                         "Blowing Sand Soil Dirt", "Unknown"), 
             selected = "Clear")



checkboxGroupInput(inputId = "Violation1_Drv1", 
                   label = h4("Violation Issued | Driver 1"), 
                   choices = c("Inattention Distraction", "Failed To Keep In Proper Lane",
                               "Disregarded Traffic Signal", "Unsafe Lane Change",
                               "Speed To Fast For Conditions","Other","Made Improper Turn",
                               "Followed Too Closely","Did Not Use Crosswal", "Other","Unknown"), 
                   selected = "Inattention Distraction")


checkboxGroupInput(inputId = "Violation1_Drv2", 
                   label = h4("Violation Issued | Driver 2"), 
                   choices = c("Inattention Distraction", "Failed To Keep In Proper Lane",
                               "Disregarded Traffic Signal", "Unsafe Lane Change",
                               "Speed To Fast For Conditions","Other","Made Improper Turn",
                               "Followed Too Closely","Did Not Use Crosswal","No Improper Action", "Other","Unknown"), 
                   selected = "Inattention Distraction")

```


```{r}
print(dat)
```

## Row

### Number of Crashes

```{r}
renderValueBox({
  
  d2 <- dat %>%
    filter(Age_Drv1 >= input$d1age[1],
           Age_Drv1 <= input$d1age[2], 
           Age_Drv2 >= input$d2age[1],
           Age_Drv2 <= input$d2age[2], 
           Gender_Drv1 %in% input$d1gender, 
           Gender_Drv2 %in% input$d2gender, 
           Unittype_One %in% input$d1pedcy, 
           Unittype_Two %in% input$d2pedcy )
  
  crashes <- count(d2)
  
  valueBox(crashes, 
           icon = "fa-solid fa-car-burst",
           color = ifelse(test = crashes > 50, 
                          yes = "danger", 
                          no = "primary") )
  
})

```

### Total Injuries

```{r}
renderValueBox({
  
  d2 <- dat %>%
    filter(Age_Drv1 >= input$d1age[1],
           Age_Drv1 <= input$d1age[2], 
           Age_Drv2 >= input$d2age[1],
           Age_Drv2 <= input$d2age[2], 
           Gender_Drv1 %in% input$d1gender, 
           Gender_Drv2 %in% input$d2gender, 
           Unittype_One %in% input$d1pedcy, 
           Unittype_Two %in% input$d2pedcy)
  
  total.injuries <- sum(d2$Totalinjuries)
  
  valueBox(total.injuries, 
           icon = "fa-solid fa-user-injured",
           color = ifelse(test = total.injuries > 30, 
                          yes = "danger", 
                          no = "primary" ))

  })

```

### Total Fatalities

```{r}
renderValueBox({
  
  d2 <- dat %>%
    filter(Age_Drv1 >= input$d1age[1],
           Age_Drv1 <= input$d1age[2], 
           Age_Drv2 >= input$d2age[1],
           Age_Drv2 <= input$d2age[2], 
           Gender_Drv1 %in% input$d1gender, 
           Gender_Drv2 %in% input$d2gender, 
           Unittype_One %in% input$d1pedcy, 
           Unittype_Two %in% input$d2pedcy)

  total.fatalities <- sum(d2$Totalfatalities)
  
  valueBox(total.fatalities, 
           icon = "fa-solid fa-skull",
           color = ifelse(test = total.fatalities > 10, 
                          yes = "danger", 
                          no = "primary"))
  
})

```

## Outputs

### Weather and Light condition

```{r}
renderLeaflet({
  
  
  filtered_data <- dat %>%
    filter((input$Lightcondition == "All" | Lightcondition == input$Lightcondition) &
           (input$Weather == "All" | Weather == input$Weather))
  
  col.vec <- ifelse(filtered_data$nohurt, 
                    "gray25", 
                    ifelse(filtered_data$inj, 
                           "blue", 
                           "red"))  
  
  point.size <- filtered_data$Totalinjuries + filtered_data$Totalfatalities
  
  crash.details <- paste0("Time: ", filtered_data$DateTime, "<br>",
                          "Total Fatalities: ", filtered_data$Totalfatalities, "<br>",
                          "Total Injuries: ", filtered_data$Totalinjuries, "<br>",
                          "Collision type: ", filtered_data$Collisionmanner)
  
  tempe <- leaflet(filtered_data) %>% 
    addProviderTiles("CartoDB.Positron") %>%
    setView(lng = -111.9278, lat = 33.4265, zoom = 13)
  
  tempe %>% 
    addCircles(lng = ~Longitude, 
               lat = ~Latitude,
               fillColor = ~col.vec, 
               fillOpacity = 0.5, 
               stroke = FALSE, 
               radius = ~50 * (1 + 0.33 * point.size),
               popup = ~crash.details) %>% 
    addLegend("topright",
              colors = c("red", "blue"),
              labels = c("Fatal", "Injuries"),
              title = "Weather Severity",
              opacity = 1)
  
})
```

# About

## Row

### About this Dashboard

Data used for this Dashboard: Click [Here](https://data.tempe.gov/)! The intended use of this dashboard is to explore the relationships between different elements and accidents. This is important to analyze to influence policies that can prevent harm and fatalities on the road.

Email: [Iwilliams78\@student.gsu.edu](mailto:Iwilliams78@student.gsu.edu){.email}

### Dashboard Author

Isis Williams

## Row

DATA DICTIONARY

```{r}

url.dd <- paste0("https://raw.githubusercontent.com",
                 "/DS4PS/cpp-526-fall-2019/master/l",
                 "abs/final-project/TempeTrafficAcc",
                 "identsDataDictionary.csv")

data.dictionary <- read.csv(url.dd, 
                            stringsAsFactors = FALSE)

data.dictionary$description <- stringi::stri_trans_general(data.dictionary$description,
                                                           "latin-ascii")

data.dictionary %>%
  select(column, description) %>%
  pander()

```

# Data

```{r}

# library( DT )

these.buttons <- c('copy', 'csv', 'pdf', 'print')

renderDataTable({
  
  datatable(dat[1:100, ], 
            filter = 'bottom', 
            rownames = FALSE, 
           #options=list( pageLength=5, autoWidth=TRUE ),
            fillContainer = TRUE, 
            style = "bootstrap",
            class = 'table-condensed table-striped',
            extensions = 'Buttons', 
            options = list(dom = 'Bfrtip', 
                           buttons=these.buttons))

  })

```
